---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/ITSLeeds/RpackageTemplate.svg?branch=master)](https://travis-ci.org/ITSLeeds/RpackageTemplate) [![Coverage status](https://codecov.io/gh/ITSLeeds/RpackageTemplate/branch/master/graph/badge.svg)](https://codecov.io/github/ITSLeeds/RpackageTemplate?branch=master) [![Build status](https://ci.appveyor.com/api/projects/status/gqp3smc04as3qg85?svg=true)](https://ci.appveyor.com/project/layik/RpackageTemplate-05ana) [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)


# RpackageTemplate

Template to form the basis of ITSLeeds R packages

## Installation

Install the package with **remotes** as follows:

```{r install, eval=FALSE}
install.packages("remotes") # If you do not already have the remotes package
remotes::install_github("ITSleeds/RpackageTemplate")
```

## Usage

Example of how the package should be used


## Acknowledgement

Acknowledge all the fine people who helped build this package.

## Contribution

Please note that the `RpackageTemplate` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.


## Package Status

This package is part of ongoing research at the University of Leeds, it is provided "as is" and is likely to be updated and changed without warning to meet the research needs of the University.
